The population of long-period exoplanets --- \\ Fully-automated discovery \& characterization of long-period transiting exoplanet candidates in the \kepler\ archive \vspace{-3\baselineskip}

### 2016-06-29 document/ms.tex
rotate table

To generate this list, we use a method much like the standard ``box least
squares'' (BLS; \dfmtodo{CITE}) procedure with a single (non-periodic) box.
First, we filter the PDC (\dfmtodo{CITE}) light curves using a running
windowed median with a half-width of \dfmtodo{how many} to remove stellar
variability.
We then compute the signal-to-noise of the depth of a 0.6~day long
transit on a grid of times spanning the full baseline of observations.

@@

For up to three candidate transit times per light curve, we select a
contiguous chunk of PDC light curve approximately centered on the proposed
transit with no more than 500 cadences \dfmtodo{check me} and compute the BIC
of each model for this data set.
The BIC for a model $k$ in the set of $K$ models is given by
\begin{eqnarray}
\mathrm{BIC}_k &=& \ln \mathcal{L}^* - \frac{J}{2}\,\log N
\end{eqnarray}
where the likelihood function $\mathcal{L}$ is evaluated at its maximum, $J$
is the number of free parameters in the model, and $N$ is the number of
data points in the data set.

For each model, we describe the data using a Gaussian Process (GP;
\dfmtodo{cite}) with a Mat\'ern-3/2 covariance and mean given by the chosen
model $m_k(t;\,\meanpars)$ parameterized by the parameter vector \meanpars.

@@

\begin{deluxetable}{cccccl}
\tabletypesize{\footnotesize}
\tablecaption{The inferred parameters for the long-period transiting exoplanet
candidates
\label{tab:table}}
\include{paramtab}
\tablenotetext{\dagger}{Candidate has two observed transits.}
\tablenotetext{a}{Included in the \citet{Wang:2015} catalog.}
\tablenotetext{b}{Included in the \citet{Uehara:2016} catalog.}
\end{deluxetable}

\begin{figure*}[p]~\\
\begin{center}
\include{lcfig}
\end{center}
\caption{%
Sections of PDC light curve centered on each candidate (black) with the
posterior-median transit model over-plotted (orange).
Candidates with two transits are folded on the posterior-median period.
\dfmfiglabel{light-curves}}
\end{figure*}

@@

The procedure for measuring the recovery rate of simulated transits is as
follows:
\begin{enumerate}
{\item First, a star is randomly selected from the target list, and the PDC
light curve and stellar properties for that star are loaded.}
{\item Planetary properties are sampled from the distributions listed in
\dfmtodo{some table} with phase uniformly distributed across the baseline of
observations. These properties are resampled until the transit is visible in
at least one non-flagged cadence.}
{\item The transit signal induced by this planet is computed and multiplied
into the PDC light curve.}
{\item The transit search method described in section \dfmtodo{some section}
(including de-trending and all automated vetting) is applied to this light
curve with the injected transit signal.}
{\item This candidate is flagged as recovered if at least one transit (within
\dfmtodo{some tolerance}) passes all the cuts imposed by the automated
vetting.}
\end{enumerate}

@@

\begin{figure*}[p]~\\
\begin{center}
\includegraphics[width=\textwidth]{figures/completeness.pdf}
\end{center}
\caption{%
\dfmfiglabel{completeness}}
\end{figure*}

>>>>

To generate this list, we use a method much like the standard ``box least
squares'' \citep[\bls;][]{Kovacs:2002} procedure with a single (non-periodic)
box.
First, we filter the \pdc\ light curves \citep{Stumpe:2012, Smith:2012}
using a running windowed median with a half-width of 2~days to remove stellar
variability.
We then compute the signal-to-noise of the depth of a 0.6~day long
transit on a grid of times spanning the full baseline of observations.

@@

For up to three candidate transit times per light curve, we select a
contiguous chunk of \pdc\ light curve approximately centered on the proposed
transit with no more than 500 cadences and compute the BIC of each model for
this data set.
The BIC for a model $k$ in the set of $K$ models is given by
\begin{eqnarray}
\mathrm{BIC}_k &=& \ln \mathcal{L}^* - \frac{J}{2}\,\log N
\end{eqnarray}
where the likelihood function $\mathcal{L}$ is evaluated at its maximum, $J$
is the number of free parameters in the model, and $N$ is the number of
data points in the data set.

For each model, we describe the data using a Gaussian Process
\citep[GP;][]{Rasmussen:2006} with a Mat\'ern-3/2 covariance and mean given by
the chosen model $m_k(t;\,\meanpars)$ parameterized by the parameter vector
\meanpars.

@@

\begin{floattable}
\begin{deluxetable}{cccccl}
\tabletypesize{\footnotesize}
\tablecaption{The inferred parameters for the long-period transiting exoplanet
candidates
\label{tab:table}}
\include{paramtab}
\tablenotetext{\dagger}{Candidate has two observed transits.}
\tablenotetext{a}{Included in the \citet{Wang:2015} catalog.}
\tablenotetext{b}{Included in the \citet{Uehara:2016} catalog.}
% \tablecomments{For the candidates with multiple transits, the
% period uncertainty is given in concise notation to be more readable}
\end{deluxetable}
\end{floattable}

\begin{figure*}[p]~\\
\begin{center}
\include{lcfig}
\end{center}
\caption{%
Sections of \pdc\ light curve centered on each candidate (black) with the
posterior-median transit model over-plotted (orange).
Candidates with two transits are folded on the posterior-median period.
\dfmfiglabel{light-curves}}
\end{figure*}

@@

The procedure for measuring the recovery rate of simulated transits is as
follows:
\begin{enumerate}
{\item First, a star is randomly selected from the target list, and the \pdc\
light curve and stellar properties for that star are loaded.}
{\item Planetary properties are sampled from the distributions listed in
\dfmtodo{some table} with phase uniformly distributed across the baseline of
observations. These properties are resampled until the transit is visible in
at least one non-flagged cadence.}
{\item The transit signal induced by this planet is computed and multiplied
into the \pdc\ light curve.}
{\item The transit search method described in section \dfmtodo{some section}
(including de-trending and all automated vetting) is applied to this light
curve with the injected transit signal.}
{\item This candidate is flagged as recovered if at least one transit (within
\dfmtodo{some tolerance}) passes all the cuts imposed by the automated
vetting.}
\end{enumerate}

@@

\begin{figure*}[p]~\\
\begin{center}
\includegraphics[width=\textwidth]{figures/completeness.pdf}
\end{center}
\caption{%
The completeness of the search procedure described here as a function of
period and radius.
In each bin, the completeness (in percent) is given with the associated
sampling uncertainty.
The projected histograms show the integrated completeness as independent
functions of period and radius.
\dfmfiglabel{completeness}}
\end{figure*}
